R Tools for Obspack, Receptors and Footprints (rtorf)

### 2024-08-20 README.Rmd
site

```{r sfsave, echo = FALSE, message=FALSE}
library(sf)
sdft <- st_as_sf(dft[stat == "mean"], 
                 coords = c("longitude", "latitude"), 
                 crs = 4326)
sdft$value <- sdft$value*1e09
png("man/figures/plotsf.png", width = 2000, height = 1500, res = 200)
plot(sdft["value"], 
     reset = FALSE, 
     axes = TRUE, 
     graticule = TRUE,
     pch = 16, 
     cex = 1.5, 
     pal = cptcity::lucky(colorRampPalette = T), #random
     main = NULL)
maps::map(add = T)
dev.off()
```

@@

![](man/figures/plotsf.png)

@@

```{r plot1, tidy = TRUE, dpi=300, fig.cap="First two sites in ObsPack"}
obs_plot(dt = df[site_name %in% usites], 
         time = "time", 
         yfactor = 1e9, 
         cex = 0.5,
         verbose = FALSE)
```

>>>>

(run it locally)

@@

@@

(run it locally)

```{r plot1, tidy = TRUE, dpi=300, fig.cap="First two sites in ObsPack", eval = F}
obs_plot(dt = df[site_name %in% usites], 
         time = "time", 
         yfactor = 1e9, 
         cex = 0.5,
         verbose = FALSE)
```
